High-Performance Primitives for Distributed Memory Architectures using Asynchronous Events

### 2012-11-12 doc/llr-pldi2013/interface.tex
got rid of an old paragraph that was in the middle of a new one

Lines 39-61 of Figure~\ref{fig:runtimeapi} show a subset of the interface for physical regions.  
Each memory in the machine's memory hierarchy is named by a {\tt Memory} object (line 39).
The next object is a {\tt PhysicalRegion} object (line 44), which contains information about the
maximum number and size of the elements within the region (line 48) and handles dynamic allocation
within the region (lines 51-52), but does not contain any storage for the element data.  Instead,
element data is stored in on or more {\tt RegionInstance} objects (line 59), each of which can be
created in an arbitrary {\tt Memory} (line 54).

A {\tt ptr\_t} value returned by the {\tt alloc}
method may be used to access the corresponding element in any of the instances of the region (line 62).
This
allows the creation of irregular data structures within physical regions.  The {\tt ptr\_t} values can
be safely stored in a region, and need not be changed when data is copied from one instance to another.
In common cases, this is as cheap as array-addressing calculations, so the overhead is minimal.
When more than one instance exists for a region, the client is responsible for maintaining coherence
of the data between the regions.  This is typically achieved through the use of instance-to-instance
copy operations (line 63) that use the producer task's completion event as a prerequisite and provide
their own completion event as a prerequisite for the consumer task.
defines a class of
regions.  Physical regions that belong to that class are created with the {\tt create\_instance}
method (line 51) and represented by {\tt RegionInstance} objects (line 56).  When creating a physical
region the client specifies the memory in which the physical region is
to be allocated.  To maintain performance transparency, a new physical region can only be allocated
if the memory has sufficient capacity.
There is no automatic coherence of data between physical regions in the
same class.  It is the client's responsibility to manage data coherence using copies
between physical regions (line 59).  Like other operations copies can be
predicated on an event and return an event corresponding to completion.  When a copy operation is
the last use of a particular instance, the destruction of that instance can also be requested and made
dependent on the copy operation's event, allowing the runtime to reclaim the memory as soon as (but no
sooner than) possible.

>>>>

Lines 39-61 of Figure~\ref{fig:runtimeapi} show a subset of the interface for physical regions.  
Each memory in the machine's memory hierarchy is named by a {\tt Memory} object (line 39).
The next object is a {\tt PhysicalRegion} object (line 44), which contains information about the
maximum number and size of the elements within the region (line 48) and handles dynamic allocation
within the region (lines 51-52), but does not contain any storage for the element data.  Instead,
element data is stored in one or more {\tt RegionInstance} objects (line 59), each of which can be
created in an arbitrary {\tt Memory} (line 54).  To maintain performance transparency, there is no
use of virtual memory - each {\tt Memory} is sized based on physical capacity and a new physical
instance can only be allocated if sufficient space remains.

A {\tt ptr\_t} value returned by the {\tt alloc}
method may be used to access the corresponding element in any of the instances of the region (line 62).
This
allows the creation of irregular data structures within physical regions.  The {\tt ptr\_t} values can
be safely stored in a region, and need not be changed when data is copied from one instance to another.
In common cases, this is as cheap as array-addressing calculations, so the overhead is minimal.
When more than one instance exists for a region, the client is responsible for maintaining coherence
of the data between the regions.  This is typically achieved through the use of instance-to-instance
copy operations (line 63) that use the producer task's completion event as a prerequisite and provide
their own completion event as a prerequisite for the consumer task.  When a copy operation is
the last use of a particular instance, the destruction of that instance can also be requested and made
dependent on the copy operation's event, allowing the runtime to reclaim the memory as soon as (but no
sooner than) possible.
